---
title: "Homework.2"
author: "N'Dri Diby"
date: "2/6/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Load the data

concrete = read.csv("/Users/pm3796gb/Desktop/DSCI 425/Homework.2/Concrete.csv")

#explore the data
head(concrete)
summary(concrete)
#pairs.plus(concrete)
set.seed(1)

```

spliting the data int0 train/test set
```{r}
#split the data into train and test set
sam = sample(1:1030,size=floor(.6666*1030),replace=F)
#train = concrete[sam,]
#test = concrete[-sam,]
y = concrete$Strength
```

Fiiting the model 
```{r}
#fitting a MLR
train.mod1= lm(Strength~.,data=concrete[sam,])

#plot the model
plot(train.mod1)

summary(train.mod1)


```

predict the response

```{r}
#prediction
y.pred = predict(train.mod1,data=concrete[-sam,])

#prediction accuracy
PredAcc(concrete$Strength[-sam],y.pred)

```

stepwise model
```{r}
concrete.step = step(train.mod1)
summary(concrete.step)
plot(concrete.step)

```

Ace method
```{r}
library(acepack)
x = model.matrix(Strength~.,data=concrete)[,-1]
y=concrete$Strength
concrete.ace = ace(x,y)
concrete.ace$rsq
maceplot(x,y,concrete.ace)

```

Ace method predictors and response transormed

```{r}
#building the model
concrete.ace.trans = lm( formula=Strength~ poly(Cement,3)+poly(BlastFurn,3)+ poly(FlyAsh,2)+ Water+ poly(Superplast,2)+ poly(CourseAgg,2)+ sqrt(FineAge)+ poly(Age,2),data=concrete[sam,])

summary(concrete.ace.trans)

plot(concrete.ace.trans)

#concrete.ace.trans = lm( formula=Strength^0.333~ Cement+poly(BlastFurn,3)+ poly(FlyAsh,2)+ poly(Water,2)+ poly(Superplast,2)+ CourseAgg+ sqrt(FineAge)+ poly(Age,2),data=concrete[sam,])
```

Avas Method
```{r}

x.avas = model.matrix(Strength~.,data=concrete)[,-1]
y.avas=concrete$Strength
concrete.avas = avas(x,y)
concrete.avas$rsq
maceplot(x,y,concrete.avas)

```

```{r}
#building the model

concrete.avas.trans = lm( formula=Strength^0.333~ poly(Cement,2)+poly(BlastFurn,2)+ poly(FlyAsh,2)+ poly(Water,2)+ poly(Superplast,2)+ CourseAgg+ FineAge+ sqrt(Age),data=concrete[sam,])

summary(concrete.avas.trans)
plot(concrete.avas.trans)
```

Ceres plot

```{r}
library(car)
ceresPlots(train.mod1)

concrete.ceres = lm(Strength~ Cement+ BlastFurn+ FlyAsh+ Water+ poly(Superplast,2)+ log(Age)+CourseAgg + FineAge,data=concrete[sam,])


#lm(Strength~ Cement+ BlastFurn+ FlyAsh+ Water+ poly(Superplast,2)+ log(Age),data=concrete[sam,])

summary(concrete.ceres)
par(mfrow=c(2,2))
plot(concrete.ceres)

"this model is better than Ace and Avas"
```

Box-Cox Procedure
```{r}
y.con = concrete$Strength
powerTransform(concrete$Strength)

concrete.box = lm(log(Strength)~.,data=concrete[sam,])
summary(concrete.box)


```

lm(Strength~ Cement+ BlastFurn+ FlyAsh+ Water+ poly(Superplast,2)+ log(Age),data=concrete[sam,])

Fitting the best model
```{r}
#lm( formula=Strength~ poly(Cement,3)+poly(BlastFurn,3)+ poly(FlyAsh,2)+ Water+ poly(Superplast,2)+ poly(CourseAgg,2)+ sqrt(FineAge)+ poly(Age,2),data=concrete[sam,])

test = concrete[-sam,]
head(test)
test$Superplast = poly(test$Superplast,2)
test$Age = poly(test$Age,2)
test$Cement = poly(test$Cement,3)
test$BlastFurn = poly(test$BlastFurn,3)
test$FlyAsh = poly(test$FlyAsh,2)
test$CourseAgg = poly(test$CourseAgg,2)
test$FineAge = sqrt(test$FineAge)
ypred.ceres = predict(concrete.ceres,data=test)
PredAcc(concrete$Strength[-sam],ypred.ceres)

```


MARS degree 1

```{r}
#building the model
library(earth)
concrete.mars1 = earth(sqrt(Strength)~.,data=concrete[sam,],degree=1,nfold=5,ncross=10,keepxy = TRUE,nk=20)

summary(concrete.mars1)

plot(concrete.mars1)

#predict
ypre.masr1 = predict(concrete.mars1,newdata=concrete[-sam,])^2
PredAcc(concrete$Strength[-sam],ypre.masr1)

```



MARS degree 2

```{r}
concrete.mars2 = earth(sqrt(Strength)~.,data=concrete[sam,],degree=2,nfold=10,ncross=5,keepxy = TRUE,nk=20 )

summary(concrete.mars2)

plot(concrete.mars2)

#predict
ypre.masr2 = predict(concrete.mars2,newdata=concrete[-sam,])^2
PredAcc(concrete$Strength[-sam],ypre.masr2)

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
